Categorical and gradient aspects of wordlikeness\thanks{Thanks to Gene Buckley, Charles Yang, and audiences at NELS 43 for helpful comments.}

### 2012-11-05 1.tex
Writing on chapter 2 primarily, also added the two "MSes" and new graphs for chapter 2.

\chapter{A generative theory of phonotactic knowledge and acquisition}
\label{intro}

@@

@@

>>>>

\label{intro}

I would like to suggest that there are two types of problems that arise in developing a theory of phonotactics free of duplication. The first type of problem consists of conflicts between theoretical assumptions and the desire to eliminate duplication. If we continue to view duplication as a sort of negative heuristic, then it may be the case that the theoretical assumptions are wrong. Such a case arises in Chapter \ref{turkish} in the discussion of archiphonemic underspecification analysis of Turkish vowel harmony proposed by \citet{Clements1982}. \citeauthor{Clemenst1982} propose that all but the first vowel of a harmonic root is underspecified for backness (and in high vowels, roundness) and is filled in by rule. Since there are disharmonic roots, this rule must be ``structure-filling''. Consequently, this rule cannot account for the apparent markedness of disharmonic roots revealed by wordlikeness judgements (among other psycholinguistic tasks). If duplication is a pathology, this analysis is wrong.

Another type of problem is the ``conundrum'', an apparent fact which poses a problem for virtually any generative theorists.

pure allophony

There are a few contexts which this interacts:

- prosody
- exceptionality
- wordlikeness

@@

Nothing will be said about what \citet{Stanley1967} calls \emph{segment structure rules}, or language-specific constraints on the inventory of (archi)phonemes, since there is a great deal of overlap between competing theories. Consider possible explanations for the apparent absense of ejectives in English, It might be that English does, in a certain sense, permit underlying ejectives, but such segments are uniformly realized as plain (i.e., pulmoni) voiceless stops: in other words, the inventory is an epiphenomenon of phonological processes. Or, perhaps English lacks the features needed to contrast ejectives with plain voiceless stops, in which case the inventory is an epiphenomenon of the system of contrast. Or, perhaps the absense of ejectives follows from no particular fact, and has the grammatical status of an accidental gap. Further assumptions are needed to distinguish these analyses.

@@

The term \emph{sequence structure constraint} is now somewhat imprecise given the apparent obsolescence of boundary segments: the ``sequence structure onstraint'' that rules out onset /bn/ in English must actually be stated as a constraint militating against /\#bn/. \citep[149]{Kenstowicz1977}
